Predicting information integration in pragmatic word learning across development

### 2021-01-05 papers/full_paper/manuscript.Rmd
add word count

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "4"
  - name          : "Megan Merrick"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
  - id            : "3"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "4"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"

@@

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"

@@

Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using]. Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged]. Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested. However, most of this work is focused on online perspective taking. In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is likely easier for children [@matthews2006effect]. We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground. Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.] information by young children is even stronger: SPeaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s]. For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "2"
  - name          : "Megan Merrick"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "2"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
  - id            : "3"
    institution   : "Department of Psychology, Stanford University"

@@

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
wordcount         : "7708"

@@

What about common ground information? Before reviewing the developmental literature, we want to briefly clarify how we use the term *common ground* in this paper. In the adult literature, common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using]. Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged]. Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested. However, most of this work is focused on online perspective taking. In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is likely easier for children [@matthews2006effect]. We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground. Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources. Construed this way, evidence for the use of common ground information by young children is strong already very early in life. For example, speaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s]. For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
